The \prob

### 2013-03-20 byzantine/byzantine.tex
byz: conclusion and references

\begin{abstract}
Sometimes, in a group of computers, there will be a broken part that will tell
confusing facts to the rest of the computers in the group. If we want to be
able to trust the entire group, it must be able to ignore these confusing facts
when deciding what to do. We can talk about this situation by playing
make-believe about the heads of a fighting force from long ago, who are waiting
with their people around a bad guy city. The people must agree upon a shared
fighting plan, but can only talk to each other by sending a person who carries
a letter. However, one or more of the heads may be bad guys who will try to
confuse the others. The problem is to find a way for the good guys to talk to
each other, without knowing who the bad guys are, to make sure they can agree
on what to do anyway. We will show that, if the good guys use only
word-of-mouth, this problem is possible if and only if more than two-thirds of
the heads are good guys. This means that a single bad guy could confuse two
good guys. If the good guys use signed written letters, which means a bad guy
couldn't pretend their letter came from someone else, the problem is possible
for any number of heads and possible bad guys.
Finally we will talk about ways to use the plans that are answers to this
problem in different situations in the real world.
\end{abstract}

@@

This way of thinking about it may appear right, but you should think hard before believing such hand-waving reasoning. Although what we said is right after all, we have seen other ``ways of thinking about it'' that are totally wrong.
We know of no area in the study of computers or the study of numbers in which hand-waving reasoning could more easily lead to wrong answers than in the study of this type of problem. For a stronger way of thinking about why this isn't possible, you should read [3]. % TODO cite
Using this answer, we can show that no plan can work for a given number of heads if one third of them are bad guys.
% Omitted: Albanian generals contradiction proof.

@@

\section{Groups of computers that you can trust}

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{citations}

>>>>

\begin{abstract}
Sometimes, in a group of computers, there will be a broken part that will tell
confusing facts to the rest of the computers in the group. If we want to be
able to trust the entire group, it must be able to ignore these confusing facts
when deciding what to do. We can talk about this situation by playing
make-believe about the heads of a fighting force from long ago, who are waiting
with their people around a bad guy city. The people must agree upon a shared
fighting plan, but can only talk to each other by sending a person who carries
a letter. However, one or more of the heads may be bad guys who will try to
confuse the others. The problem is to find a way for the good guys to talk to
each other, without knowing who the bad guys are, to make sure they can agree
on what to do anyway. We will show that, if the good guys use only
word-of-mouth, this problem is possible if and only if more than two-thirds of
the heads are good guys. This means that a single bad guy could confuse two
good guys. If the good guys use signed written letters, which means a bad guy
couldn't pretend their letter came from someone else, the problem is possible
for any number of heads and possible bad guys.
% Finally we will talk about ways to use the plans that are answers to this problem in different situations in the real world.
\end{abstract}

@@

This way of thinking about it may appear right, but you should think hard before believing such hand-waving reasoning. Although what we said is right after all, we have seen other ``ways of thinking about it'' that are totally wrong.
We know of no area in the study of computers or the study of numbers in which hand-waving reasoning could more easily lead to wrong answers than in the study of this type of problem. For a stronger way of thinking about why this isn't possible, you should read [3].
Using this answer, we can show that no plan can work for a given number of heads if one third of them are bad guys.
% Omitted: Albanian generals contradiction proof.

@@

% omitted: \section{Groups of computers that you can trust}

\section{Closing Words}

We have presented several answers to the \prob, in several different situations.
The plans in these answers can take a lot of time to run and can also need a lot of letters to be sent.
Both the Spoken Words plan and the Signed Letters plan might need each order to be sent more than $m$ times, where $m$ is the number of bad guys.

In other words, each head may have to wait for orders that came from the controlling head and were then passed on by $m$ other heads.
Other people who study computers
have shown that this must be true for any answer that can be okay with with $m$ bad guys, so our answers are as good as possible.

The Spoken Words plan and the Signed Letters plan need you to send up to $(n-1)$ times $(n-2)$ times $(n-m-1)$ letters or words. You can make the number of different times you need to send lower by putting letters or words together and sending them at the same time.
It may also be possible to lower how much you actually need to say at all, but we have not studied this enough to be sure.
However, we expect that a large number of letters will still be needed.

Making a group of computers that you can trust even when there might be bad guys that try to confuse you in whatever way they want is a hard problem. It seems like any plan to do this will need to take a lot of time or space.
The only way to make it need less is to start supposing things about the way things might go wrong.
One such way is to suppose that a computer may stop responding but will never respond with something wrong.
However, when you need to trust your computers very very much, you can't suppose that sort of thing, and you need to spend all time and space it takes to solve the \prob.

% Bibliography
\section*{PAST THINGS THAT WE BUILT ON}

{\small
\begin{tabular}{p{0.3em}p{0.95\textwidth}}
1.& {\sc Monroe, R.} Up Goer Five. {\em XKCD Computer Funny Pictures,} \url{http://xkcd.com/1133/}, 2013.\\
2.& {\sc Sanderson, T.} The Up-Goer Five Word-Writing Computer Game. \url{http://splasho.com/upgoer5/}, 2013.\\
3.& {\sc Pease, M., Shostak, R., and Lamport, L.} Reaching a Way to Agree Even When There are Faults. {\em J. ACM 27,} 2 (Month Four 1980), 228-234.
\end{tabular}
}
